---
title: "Group 05 CA pollution burden"
author: "Logan Babcock, Jack Miller"
date: "November 12, 2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# attach packages

library(janitor)
library(here)
library(tidyverse)

```

```{r}
# read in data

ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r message = FALSE, warning = FALSE}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() + 
  scale_fill_gradient(low = "red", high = "yellow") +
  labs(x = "White Population Percentage", y = "CalEnviroScreen Pollution Burden Score", caption = "Figure 1 shows the relationship between the percent of the US population that is white and the community pollution burden score. The pollution burden score is a function of exposure to harmful environmental impacts and the community's socioeconomic characteristics.") +
  theme_minimal()
```

The hexagon plot depicts an overall negative trend between the White population percentage and the CaEnviroScreen Pollution Burden Score. This means that a higher White population percentage relates to a lower CalEnviroScreen Pollution Burden Score.  

Data Citation: United States 2010 Census; CalEnviroScreen 3.0 score from the Office of Environmental Health Hazard Assessment (OEHHA)
